%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rahma Seid} \\ \vspace{1pt}
    \small 615-482-7068 $|$ \href{mailto:x@x.com}{\underline{seidrahma6@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/rahma-seid/}{\underline{linkedin.com/in/rahma-seid}} $|$
    \href{https://github.com/rahmaseid}{\underline{github.com/rahmaseid}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Middle Tennessee State University}{Murfreesboro, TN}
      {Bachelor of Science in Computer Science, Minor in Data Science}              {Expected: Dec. 2025}

      \resumeSubItem{\textbf{Awards}: HackMT 3rd Place Award (2023), Grace Hopper Celebration Scholarship (2022)  }

      \resumeSubItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Computer Systems, Discrete Structures, Assembly \& Computer Organization, Data Cleansing \& Feature Engineering, Database Management Systems, Web Technologies, Applied Predictive Modeling  }

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{Aug. 2023 -- Oct. 2023}
      {Voorhees Engineering Technology Lab}{Murfreesboro, TN}
      \resumeItemListStart
        \resumeItem{Developed interactive data dashboards in \textbf{Excel}, streamlining analysis of machine-generated irrigation data and reducing evaluation time by \textbf{40\%}, improving decision-making for water usage. }
        \resumeItem{Utilized \textbf{high-resolution imaging systems} to improve soil moisture trend accuracy by \textbf{25\%}, enabling more precise agricultural interventions. }
        \resumeItem{Engineered a pipeline to convert raw sensor data into actionable insights, enhancing the lab’s ability to evaluate environmental patterns for smart irrigation planning. }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeSubheading
          {\textbf{\href{https://github.com/rahmaseid/MixItUp}{Mixtape Web App}} $|$ \emph{PHP, MySQL, JavaScript, HTML/CSS}}{April 2025 -- May 2025} {Team Lead \& Backend Developer – Web Technologies Project}{}
          \resumeItemListStart
            \resumeItem{Led a \textbf{full-stack development team} in creating a dynamic web app where users can generate, save, and play custom music mixtapes using \textbf{YouTube video metadata}.  }
            \resumeItem{Designed and implemented the \textbf{MySQL relational database schema} linking users, songs, and playlists, enabling structured and scalable data storage. }
            \resumeItem{Developed backend logic in \textbf{PHP} to handle playlist creation, storage, and retrieval, ensuring seamless integration with the frontend. }
            \resumeItem{Collaborated with frontend developers to maintain consistent \textbf{data flow} and \textbf{user experience} across features such as playlist history, theme switching, and playback controls.}
          \resumeItemListEnd
      \resumeSubheading
          {\textbf{\href{https://github.com/rahmaseid/CSCI-4560-Final-Project}{Personal Budget App}} $|$ \emph{PHP, MySQL, Docker, XAMPP}}{Jan. 2025 -- April 2025} {Backend Developer - Database Management Systems Project}{}
          \resumeItemListStart
            \resumeItem{Engineered the backend in \textbf{PHP} and designed a normalized \textbf{MySQL} database schema using \textbf{phpMyAdmin} with relational integrity, enabling secure storage and retrieval of user data across budgeting, transactions, and bill management features. }
            \resumeItem{Collaborated on a 3-person team to build and deploy a web-based personal finance app using \textbf{HTML/CSS} and \textbf{Docker},  integrating goal-based savings tracking, automated bill reminders, and expense forecasting tools.}
            \resumeItem{Enabled advanced financial features such as \textbf{goal-based savings tracking}, \textbf{automated bill reminders}, and \textbf{expense forecasting}, improving users’ budgeting insight and control.}
          \resumeItemListEnd
      \resumeSubheading
          {\textbf{\href{https://github.com/rahmaseid/CSCI_3240-PacMan-Final_Project}{Pac-Man Game} $|$ \emph{C, Socket Programming}}}{Nov. 2024 -- Dec. 2024}{Computer Systems Project}{}
          \resumeItemListStart
            \resumeItem{Built a \textbf{multiplayer Pac-Man-style game} in \textbf{C} using \textbf{client-server architecture}, offering a responsive and scalable real-time gaming experience. }
            \resumeItem{Implemented s\textbf{ocket programming} and \textbf{multi-threading} to maintain concurrent player sessions, reducing latency and enhancing gameplay reliability. }
            \resumeItem{Resolved synchronization issues using \textbf{mutexes} and \textbf{conditional variables}, improving game stability and ensuring consistent state management during multiplayer interactions.}
          \resumeItemListEnd
        \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL, TypeScript, HTML/CSS, PHP} \\
     \textbf{Frameworks}{: React, React Native, Flutter} \\
     \textbf{Developer Tools}{: GitHub, Replit, Jupyter Notebook, Android Studio, VS Code, Expo, MySQL Workbench} \\
     \textbf{Development Concepts}{: Data Structures \& Algorithms, Object-Oriented Programming (OOP) }
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
